\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2014-07-01 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex

%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
Since then it has been developed and maintained by a development team:
in alphabetical order,
Jean-Paul (Pablo) Ampuero,
Can Kangchen Bai,
Piero Basini,
Céline Blitz,
Ebru Bozda\u{g},
Emanuele Casarotti,
Joseph Charles,
Min Chen,
Percy Galvez,
Dominik Göddeke,
Vala Hjörleifsdóttir,
Sue Kientz,
Dimitri Komatitsch,
Jesús Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Matthieu Lefebvre,
Qinya Liu,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
René Matzen,
Dennis McRitchie,
Matthias Meschede,
Peter Messmer, 
David Michéa,
Surendra Nadh Somala,
Tarje Nissen-Meyer,
Daniel Peter,
Max Rietmann,
Elliott Sales de Andrade,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Jean-Pierre Vilotte,
Zhinan Xie,
Hejun Zhu.\\

>>>>

%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
Since then it has been developed and maintained by a development team:
in alphabetical order,
Jean-Paul (Pablo) Ampuero,
Kangchen Bai,
Piero Basini,
Céline Blitz,
Ebru Bozda\u{g},
Emanuele Casarotti,
Joseph Charles,
Min Chen,
Percy Galvez,
Dominik Göddeke,
Vala Hjörleifsdóttir,
Sue Kientz,
Dimitri Komatitsch,
Jesús Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Matthieu Lefebvre,
Qinya Liu,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
René Matzen,
Dennis McRitchie,
Matthias Meschede,
Peter Messmer, 
David Michéa,
Surendra Nadh Somala,
Tarje Nissen-Meyer,
Daniel Peter,
Max Rietmann,
Elliott Sales de Andrade,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Jean-Pierre Vilotte,
Zhinan Xie,
Hejun Zhu.\\
